Anisotropic in-plane thermal conductivity in multilayer silicene

### 2018-01-15 submit/paper.tex
submit to CMS

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2018-01-11 15:12:52

\documentclass[aps,prb,twocolumn,showpacs,amsmath,amssymb]{revtex4-1}

\preprint{APS/123-QED}

@@

\usepackage{multirow}
\usepackage{epsfig}
\usepackage{amssymb}

\newcommand{\angstrom}{\mbox{\normalfont\AA}}

@@

\title{Anisotropic in-plane thermal conductivity in multilayer silicene}
\author{Yang Zhou${}^{1,3}$}
\author{Zhi-Xin Guo${}^{2,1}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen${}^{1}$}
\author{Hong-Jun Xiang${}^{1}$}
\author{Xin-Gao Gong${}^{1,3}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
}
\begin{abstract}
  We systematically study thermal conductivity of multilayer silicene by means of Boltzmann Transportation Equation (BTE) method.  We find that their thermal conductivity strongly depends on the surface structures. Thermal conductivity of bilayer silicene varies from $3.31$ W/mK to $57.9$ W/mK with different surface structures. Also, the $2\times1$ surface reconstruction induces unusual large thermal conductivity anisotropy, which reaches 70\%  in a four-layer silicene.  We also find that the anisotropy decreases with silicene thickness increasing, owing to the significant reduction of thermal conductivity in the zigzag direction and its slight increment  in the armchair direction.
  Finally, we find that both the phonon-lifetime anisotropy and the phonon-group-velocity  anisotropy contribute to the thermal conductivity anisotropy of multilayer silicene.
  These findings could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nanomaterials  with surface reconstructions in the future.

@@

The atomic structures of multilayer silicene that were predicted to be stable by Guo \emph{et al}\cite{Guo2015Structural} are shown in Fig.\ref{fig:structures}. For convenience, we define the names of these structures as "nlxs", where "n" is a pure number, representing the number of layers, "l" means layer, "x" distinguishes different structures (concrete 1, 2, 3 etc. ) and "s"="a" or "z", corresponds to the silicene edge along the length direction, i. e.,  "a" for armchair) and "z" for zigzag. We also show in TABLE.\ref{tab:table1} the structure names and  minimum repeat cell periodicities of these multilayer silicene.

\begin{figure}[b]
  \includegraphics[angle= 0, width=0.95\linewidth]{images/structures.eps}
  \caption{\label{fig:structures}  (color online)  Top view and side views of typical structures of multilayer silicene. The buckling Si atoms on the top layer are labeled as yellow balls, and the red balls represent the remaining Si atoms on the top layer. All the Si atoms on the bottom layer are labeled as the blue balls. The green balls represent Si atoms in the middle layers. The orientation of top view of the cells is armchair in the x direction and zigzag in the y direction in the figure. The structures exihibit obvious and pretty different surface reconsruction.}
\end{figure}

Silicene structures are fully optimized using the conjugate gradient method.  The finite displacement method (FDM) realized in Phonopy\cite{Togo2008} and Thirdorder \cite{Li2014} are applied to extract the second- and third-order force constants (FCs) respectively,  in which hundreds of  slightly displaced supercells are generated. The obtained forces are calculated and used to calculate the FCs with the numerical differential calculation. The supercells of $3 \times 3 \times 1$ primitive cells are adopted to make the in-plane dimension above 40 \angstrom, which ensure the accuracy of calculated forces. Following the previous studies\cite{Pei2013,Fu2014}, we choose Si (111) layer spacing of $3.14 \angstrom$ as the interlayer thickness d because the thickness of two dimensional silicene is hard to restrictly determined, since it's a common constant for all the structures, the conclusion is independent on the absolute value of d, so a experimental value makes sence here.

@@

\begin{figure}[b]
  \includegraphics[angle= 0, width=0.9\linewidth]{images/chi.eps}{}
  \caption{\label{fig:chi} (color online) The dependence on cutoff MPF of cummulative TC anisotropy $\chi$. $\chi$ of 2L2 structure is exactly zero and is a horizonal line at 0. For 2L1, 2L3  structures the anisotropy increase with the cutoff MPF while that of 3L1 decreases. The others show indepencece of cutoff MPF. For bilayer silicence the anisotropy comes from long wave phonons while for multilayer structure it comes from phonons of all the wave length. }
\end{figure}

@@

\begin{table*}
  \caption{\label{tab:table1}
    The thermal conductivity and its anisotropy of different multilayer silicene, along with the average heat capacity ($kJ/m^3/K$) of zigzag ( $Cv_z$) and armchair ($Cv_a$) directions, respectively. }
  \begin{ruledtabular}
    \begin{tabular}{ccccccc}
          & Minimal period
          & $\kappa_{z,\infty}$
          & $\kappa_{a,\infty}$
          & $\chi$
          & $Cv_{z}$
          & $Cv_{a}$                                                           \\
      \hline
      2L1 & $1 \times 1$             & 42.10 & 57.92 & 27.31\% & 165.8 & 166.7 \\
      2L2 & $\sqrt{2}\times\sqrt{2}$ & 31.11 & 31.11 & 0    \% & 38.44 & 38.44 \\
      2L3 & $2 \times 2$             & 3.311 & 5.624 & 41.13\% & 22.42 & 22.42 \\
      3L1 & $2 \times 1$             & 31.44 & 14.05 & 55.29\% & 52.22 & 52.46 \\
      4L1 & $2 \times 1$             & 20.37 & 6.114 & 69.98\% & 37.71 & 37.89 \\
      5L1 & $2 \times 1$             & 19.33 & 6.419 & 66.78\% & 29.17 & 29.32 \\
      6L1 & $2 \times 1$             & 17.78 & 6.527 & 63.29\% & 23.73 & 23.86 \\
      8L1 & $2 \times 1$             & 17.56 & 7.461 & 57.51\% & 17.26 & 17.36 \\
    \end{tabular}
  \end{ruledtabular}
\end{table*}

@@

The heat capacity has contribution to mugnitude difference in the structures but is not responsible for the anisotropy. To have a deep insight into the origin of anisotropy, it's helpful to investigate all the factors that contribute to thermal conductivity according to Eq.(\ref{eq:kappasum}).
We select all the phonons along  $\Gamma\rightarrow X$ and $\Gamma \rightarrow Y$ directions in Brillouin zone, and calculated their heat capacity with Eq.(\ref{eq:cv}). The averaged heat capacity of silicene structures are shown in Table.\ref{tab:table1}, where $Cv_z$ and $Cv_a$ correspond to the  heat capacity for thermal conductivity in the zigzag and armchair directions, respectively.  As one can see, although $Cv_z$ and $Cv_a$  strongly depend on the reconstructed structure and thickness of multilayer silicene, their difference in the same structure is very small. This feature shows that the thermal conductivity anisotropy is insensitive to the heat capacity.

@@

\begin{figure}[b]
  \includegraphics[width=1\linewidth]{images/tau.eps}
  \caption{\label{fig:tau} (color online)  Phonons lifetimes of multilayer silicene obtained by considering the three-phonon scattering process.  The horizonal dash line at 1.0ps is a guidence for the main contribution region of phonon frequency. Phonon lifetime doent's show obvious anisotropy in both bilayer structure and multilayer structures (except for the anmornal region of 5-7 THz in 4L1 structure). The main contribution of lifetime comes from low frequency phonons in bilayer structures while the others have relative uniform contribution from the frequency domain.  }
\end{figure}

\begin{figure}[b]
  \includegraphics[width=0.9\linewidth]{images/gv.eps}{}
  \caption{\label{fig:gv} (color online) Group velocities versus phonon frequencies in both the zigzag and armchair directions of multilayer silicene. The histogram bin width is chosen as 1.5 THz. The bilayer structures have isotropic group velocities at low frequency region and the contribution from high frequency could be ignored considering the valishment of lifetime at this region. The structure of 3-6 layers exhibit anisotropic group velocity which suggests localization of phonons.}
\end{figure}

Phonon lifetime of low frequency is much larger and anisotropic than high frequency in bilayer structures while in multilayer structures it has less denpendence on frequency. We have considered the three-phonon scattering process, where the scattering rate is obtained from the Fermi-golden's rule\cite{Li2014} under the relaxation time approximation (RTA). The iterative method was then adopted to include the cross influence of the phonon excitation, since it usually gives lager but more accurate lifetimes than the RTA. The frequency dependence of phonon lifetimes calculated with ShengBTE\cite{Li2014} are shown in Fig.\ref{fig:tau}, where the values are averaged for frequency bins to reduce complexity.  It is shown that the lifetimes of larger than 1 ps for bilayer silicene structures (2L1, 2L3) distribute on the low-frequency region, indicating the dominating contributions of low-frequency phonons to the thermal conductivity. Moreover, the lifetimes in armchair direction are obviously larger than that in zigzag direction in the low-frequency region. This feature indicates that the thermal conductivity anisotropy of bilayer silicene is attributed to the difference of phonon lifetimes in different directions.
On the other hand, the phonon lifetimes exhibit a different frequency distribution for the thicker silicene, i. e.,  $2\times1$ structures with 3-6 Si layer in thickness, where the phonon lifetimes larger than 1 ps cover both the low and high frequency regions.  This explains why the high frequency phonons contribute significantly to the thermal conductivity in the thicker silicene (Fig. \ref{fig:tc_freq}).  However, except for the 4L1 structure, the phonon lifetimes in zigzag and armchair directions are very close for the $2\times1$ structures, implying their tiny effect on the thermal conductivity anisotropy.

>>>>

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2018-01-15 17:09:48

\documentclass[review]{elsarticle}

@@

\usepackage{multirow}
\usepackage{epsfig}
\usepackage{amssymb}
\bibliographystyle{elsarticle-num}
\newcommand{\angstrom}{\mbox{\normalfont\AA}}

@@

\title{Anisotropic in-plane thermal conductivity in multilayer silicene}
\author[1,3]{Yang Zhou}
\author[2,1]{Zhi-Xin Guo\corref{correspondingauthor1}}
\author[1]{Shi-You Chen}
\author[1]{Hong-Jun Xiang}
\author[1,3]{Xin-Gao Gong\corref{correspondingauthor2}}
\cortext[correspondingauthor1]{zxguo08@hotmail.com}
\cortext[correspondingauthor2]{xggong@fudan.edu.cn}

\address[1]{Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China}
\address[2]{Department of Physics, Xiangtan University, Xiangtan 411105, China}
\address[3]{Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China}
\begin{abstract}
  We systematically study thermal conductivity of multilayer silicene by means of Boltzmann Transportation Equation (BTE) method.  We find that their thermal conductivity strongly depends on the surface structures. Thermal conductivity of bilayer silicene varies from $3.31$ W/mK to $57.9$ W/mK with different surface structures. Also, the $2\times1$ surface reconstruction induces unusual large thermal conductivity anisotropy, which reaches 70\%  in a four-layer silicene.  We also find that the anisotropy decreases with silicene thickness increasing, owing to the significant reduction of thermal conductivity in the zigzag direction and its slight increment  in the armchair direction.
  Finally, we find that both the phonon-lifetime anisotropy and the phonon-group-velocity  anisotropy contribute to the thermal conductivity anisotropy of multilayer silicene.
  These findings could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nanomaterials  with surface reconstructions in the future.

@@

The atomic structures of multilayer silicene that were predicted to be stable by Guo \emph{et al}\cite{Guo2015Structural} are shown in Fig.\ref{fig:structures}. For convenience, we define the names of these structures as "nLxs", where "n" is a pure number, representing the number of layers, "L" means layer, "x" distinguishes different structures (concrete 1, 2, 3 etc. ) and "s"="a" or "z", corresponds to the silicene edge along the length direction, i. e.,  "a" for armchair) and "z" for zigzag. We also show in TABLE.\ref{tab:table1} the structure names and  minimum repeat cell periodicities of these multilayer silicene.

\begin{figure}[b]
  \includegraphics[angle= 0, width=0.95\linewidth]{images/structures.eps}
  \caption{\label{fig:structures}  (color online)  Top view and side views of typical structures of multilayer silicene. The buckling Si atoms on the top layer are labeled as yellow balls, and the red balls represent the remaining Si atoms on the top layer. All the Si atoms on the bottom layer are labeled as the blue balls. The green balls represent Si atoms in the middle layers. The orientation of top view of the cells is armchair in the x direction and zigzag in the y direction in the figure. The structures exhibit obvious and pretty different surface reconsruction.}
\end{figure}

Silicene structures are fully optimized using the conjugate gradient method.  The finite displacement method (FDM) realized in Phonopy\cite{Togo2008} and Thirdorder \cite{Li2014} are applied to extract the second- and third-order force constants (FCs) respectively,  in which hundreds of  slightly displaced supercells are generated. The obtained forces are calculated and used to calculate the FCs with the numerical differential calculation. The supercells of $3 \times 3 \times 1$ primitive cells are adopted to make the in-plane dimension above 40 \angstrom, which ensure the accuracy of calculated forces. Following the previous studies\cite{Pei2013,Fu2014}, we choose Si (111) layer spacing of $3.14 \angstrom$ as the interlayer thickness d because the thickness of two dimensional silicene is hard to strictly  determined, since it's a common constant for all the structures, the conclusion is independent on the absolute value of d, so a experimental value makes sense here.

@@

\begin{figure}[b]
  \includegraphics[angle= 0, width=0.9\linewidth]{images/chi.eps}{}
  \caption{\label{fig:chi} (color online) The dependence on cutoff MPF of cummulative TC anisotropy $\chi$. $\chi$ of 2L2 structure is exactly zero and is a horizonal line at 0. For 2L1, 2L3  structures the anisotropy increase with the cutoff MPF while that of 3L1 decreases. The others show independence of cutoff MPF. For bilayer silicene the anisotropy comes from long wave phonons while for multilayer structure it comes from phonons of all the wave length. }
\end{figure}

@@

\begin{table*}
  \caption{\label{tab:table1}
    The thermal conductivity and its anisotropy of different multilayer silicene, along with the average heat capacity ($kJ/m^3/K$) of zigzag ( $Cv_z$) and armchair ($Cv_a$) directions, respectively. }

  \begin{tabular}{ccccccc}
        & Minimal period
        & $\kappa_{z,\infty}$
        & $\kappa_{a,\infty}$
        & $\chi$
        & $Cv_{z}$
        & $Cv_{a}$                                                           \\
    \hline
    2L1 & $1 \times 1$             & 42.10 & 57.92 & 27.31\% & 165.8 & 166.7 \\
    2L2 & $\sqrt{2}\times\sqrt{2}$ & 31.11 & 31.11 & 0    \% & 38.44 & 38.44 \\
    2L3 & $2 \times 2$             & 3.311 & 5.624 & 41.13\% & 22.42 & 22.42 \\
    3L1 & $2 \times 1$             & 31.44 & 14.05 & 55.29\% & 52.22 & 52.46 \\
    4L1 & $2 \times 1$             & 20.37 & 6.114 & 69.98\% & 37.71 & 37.89 \\
    5L1 & $2 \times 1$             & 19.33 & 6.419 & 66.78\% & 29.17 & 29.32 \\
    6L1 & $2 \times 1$             & 17.78 & 6.527 & 63.29\% & 23.73 & 23.86 \\
    8L1 & $2 \times 1$             & 17.56 & 7.461 & 57.51\% & 17.26 & 17.36 \\
  \end{tabular}
\end{table*}

@@

The heat capacity has contribution to magnitude difference in the structures but is not responsible for the anisotropy. To have a deep insight into the origin of anisotropy, it's helpful to investigate all the factors that contribute to thermal conductivity according to Eq.(\ref{eq:kappasum}).
We select all the phonons along  $\Gamma\rightarrow X$ and $\Gamma \rightarrow Y$ directions in Brillouin zone, and calculated their heat capacity with Eq.(\ref{eq:cv}). The averaged heat capacity of silicene structures are shown in Table.\ref{tab:table1}, where $Cv_z$ and $Cv_a$ correspond to the  heat capacity for thermal conductivity in the zigzag and armchair directions, respectively.  As one can see, although $Cv_z$ and $Cv_a$  strongly depend on the reconstructed structure and thickness of multilayer silicene, their difference in the same structure is very small. This feature shows that the thermal conductivity anisotropy is insensitive to the heat capacity.

@@

\begin{figure}[b]
  \includegraphics[width=1\linewidth]{images/tau.eps}
  \caption{\label{fig:tau} (color online)  Phonons lifetimes of multilayer silicene obtained by considering the three-phonon scattering process.  The horizonal dash line at 1.0ps is a guidance for the main contribution region of phonon frequency. Phonon lifetime doesnt's show obvious anisotropy in both bilayer structure and multilayer structures (except for the abnmornal region of 5-7 THz in 4L1 structure). The main contribution of lifetime comes from low frequency phonons in bilayer structures while the others have relative uniform contribution from the frequency domain.  }
\end{figure}

\begin{figure}[b]
  \includegraphics[width=0.9\linewidth]{images/gv.eps}{}
  \caption{\label{fig:gv} (color online) Group velocities versus phonon frequencies in both the zigzag and armchair directions of multilayer silicene. The histogram bin width is chosen as 1.5 THz. The bilayer structures have isotropic group velocities at low frequency region and the contribution from high frequency could be ignored considering the vanishment of lifetime at this region. The structure of 3-6 layers exhibit anisotropic group velocity which suggests localization of phonons.}
\end{figure}

Phonon lifetime of low frequency is much larger and anisotropic than high frequency in bilayer structures while in multilayer structures it has less dependence on frequency. We have considered the three-phonon scattering process, where the scattering rate is obtained from the Fermi-golden's rule\cite{Li2014} under the relaxation time approximation (RTA). The iterative method was then adopted to include the cross influence of the phonon excitation, since it usually gives lager but more accurate lifetimes than the RTA. The frequency dependence of phonon lifetimes calculated with ShengBTE\cite{Li2014} are shown in Fig.\ref{fig:tau}, where the values are averaged for frequency bins to reduce complexity.  It is shown that the lifetimes of larger than 1 ps for bilayer silicene structures (2L1, 2L3) distribute on the low-frequency region, indicating the dominating contributions of low-frequency phonons to the thermal conductivity. Moreover, the lifetimes in armchair direction are obviously larger than that in zigzag direction in the low-frequency region. This feature indicates that the thermal conductivity anisotropy of bilayer silicene is attributed to the difference of phonon lifetimes in different directions.
On the other hand, the phonon lifetimes exhibit a different frequency distribution for the thicker silicene, i. e.,  $2\times1$ structures with 3-6 Si layer in thickness, where the phonon lifetimes larger than 1 ps cover both the low and high frequency regions.  This explains why the high frequency phonons contribute significantly to the thermal conductivity in the thicker silicene (Fig. \ref{fig:tc_freq}).  However, except for the 4L1 structure, the phonon lifetimes in zigzag and armchair directions are very close for the $2\times1$ structures, implying their tiny effect on the thermal conductivity anisotropy.
